
\label{chap:bib}
\section{Bibliography}

\begin{enumerate}

\item D. Yadav, S. Sanchez-Cuadrado, and J. Morato, “Optical Character Recognition for Hindi Language Using a Neural-network Approach,” Journal of Information Processing Systems, vol. 9, no. 1, pp. 117–140, Mar. 2013.

\item K. Dutta, P. Krishnan, M. Mathew and C. V. Jawahar, "Towards Spotting and Recognition of Handwritten Words in Indic Scripts," 2018 16th International Conference on Frontiers in Handwriting Recognition (ICFHR), 2018, pp. 32-37, doi: 10.1109/ICFHR-2018.2018.00015.

\item Nafiz Arica , Student Member , Fatos T. Yarman-vural , Senior Member, "Optical Character Recognition for Cursive Handwriting", IEEE TRANSACTIONS ON PATTERN ANALYSIS AND MACHINE INTELLIGENCE, VOL. 24, NO. 6, JUNE 2002

\item Gunna, S., Saluja, R., Jawahar, C.V. (2021). Transfer Learning for Scene Text Recognition in Indian Languages. In: Barney Smith, E.H., Pal, U. (eds) Document Analysis and Recognition – ICDAR 2021 Workshops. ICDAR 2021. Lecture Notes in Computer Science(), vol 12916. Springer, Cham.

\item Abhishek Mehta, Dr. Subhashchdra Desai, Dr. Ashish Chaturvedi, 2021, Hindi Handwritten Character Recognition from Digital Image using Deep Learning Neural Network, INTERNATIONAL JOURNAL OF ENGINEERING RESEARCH & TECHNOLOGY (IJERT) ICRADL – 2021 (Volume 09 – Issue 05)

\item Nisha Goyal1 , Er. Shilpa Jain, "Optimized Hindi Script Recognition using OCR Feature Extraction Technique", International Journal of Advanced Research in Computer and Communication Engineering Vol. 4, Issue 8, August 2015.

\item Bairagi, Prasanta Pratim. “Optical Character Recognition for Hindi.” (2018).

\end{enumerate}